Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-22 src/tex/ms.tex
Update ms.tex

% Section guide
In Sec.~\ref{sec:Method}, we describe the modification we made to the waveform model, and mention the configuration we used in the PE.
In Sec.~\ref{sec:Results}, we show the combined result of the PE, and present the constrain on the GW amplitude birefringence we obtained.
In Sec.~\ref{sec:Discussion}, we discuss the limitation of this study, and provide suggestions for future studies.

@@

\section{Acknowledgements}
\label{sec:Acknowledgements}

>>>>

% Section guide
In Sec.~\ref{sec:Method}, we describe the modification we made to the waveform model, and mention the configuration we used in the PE.
In Sec.~\ref{sec:Results}, we show the combined result of the PE, and present the constrain on GW amplitude birefringence we obtained.
In Sec.~\ref{sec:Discussion}, we discuss the limitation of this study, and provide suggestions for future studies.

@@

\section{Acknowledgements}
\label{sec:Acknowledgements}
M.~I., K.~W.~K.~W.~ and W.~M.~F.~ are funded by the Center for Computational Astrophysics at the Flatiron Institute, which is supported by the Simons Foundation.
The computational resources used in this work were provided by the Flatiron Institute.
